---
title: "R Notebook"
output: html_notebook
---

Set things up 

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(primer)
```

Working through [Chapter 1](https://hankstevens.github.io/Primer-of-Ecology/theory.html) of [A Primer of Ecology with R](https://hankstevens.github.io/Primer-of-Ecology/index.html) by Hank Stevens.

## Metabolic theory of ecology

Let's plot the Kleiber curve using the `curve()` function which can plot any curve that can be expressed as a function of x.

```{r}
## using curve, let your variable be 'x'.
curve(1*x, from = .01, to=100, ylab = "Metabolic rate (B)",
      xlab="Body mass (M)", lty=3)
curve(x^(3/4), from = .01, to = 100, add=TRUE)
```
And look at mass-specific metabolic rate, which is generally basal metabolism divided by body mass.

The rule is that *mass-specific metabolic rate declines with organisms mass raised to the negative one-quarter power*

```{r}
eq1 = function(M, a){a*M^-0.25} # create the function, F(M)
ggplot(data=data.frame(x=c(0.1, 100)), aes(x=x) ) + 
  stat_function(fun=eq1, geom="line", args=list(a=1)) + 
  xlab("Mass (M)") + ylab("Mass-specific metabolic rate (B/M)")

```

